Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

        \subsubsection{Reproduction} This process will select random pairs of
        individuals to evaluate their attraction as a couple, where this attraction
        will depend on fitness. The better individual's fitness, the more attractive it
        will be. Not all couples will be compatible, so reproduction will not always be
        possible. When the breeding is successful, a new pair of individuals will be
        born (offspring).

>>>>

        \subsubsection{Reproduction} In this step, we select a random pair of
        individuals and evaluate their couple's attraction, where fitness will
        be the decisive factor that impacts its value. The higher the fitness
        of the individual, the more attractive it will appear to fellow
        individuals. As a consequence of the previous concept, we can
        anticipate that not all couples will produce offspring, meaning
        reproduction will not always be successful.
